Software Ticket Quality

### 2017-11-15 proposal/mprop.tex
Add paper on software process data quality and characteristics

>>>>

\textbf{Software Process Data Quality and Characteristics}\cite{bachmann2009software}:
\begin{itemize}
  \item \textbf{What were the goals?}
    The authors are trying to investigate different software process data
    (e.g. bug tracking databases, version control systems logs) in order to
    infer quality and characteristics. Then, they want to compute measures
    and discuss the issues that arise from these observations.
  \item \textbf{What was the method?}
    They examined 6 software projects, 5 of which were open source, by extracting
    the SVN and CSV logs, as well as the content of the bug tracker databases. Then,
    they tried to link the logs with the contents of the bug tracker databases as they
    are not integrated by default. 
  \item \textbf{What did they learn?}
    Firstly, the closed source project the authors examined showed much more data
    quality as the open source counterparts, among which better average attachments 
    per bug report, better average status changes per bug report or average commits
    per bug report/developer. Moreover, the authors found that there is little linkage
    between bug reports and version control logs, thus reducing the overall traceability.
    Also, there is reduced quality in change logs as, for example, the Eclipse project
    has more than 20\% empty commit messages. In conclusion, closed source projects will
    probably exhibit improved data quality than open source ones, but data quality in general
    differs from project to project.
  \item \textbf{Relevance to our work}:
    The analysis on data quality in open/closed source projects presented in this 
    research is valuable to us as it presents various statistics on commits, bug report
    structure and quality, as well as linkage between the two. We might apply the techniques
    in our own research on ticket quality.
\end{itemize}
